The Relationship between Family Status and Academic Achievement in Children in U.S. from 2021

### 2023-03-28 outputs/paper/paper.qmd
add the survey and its link! only discussion part left!

---
title: "The Relationship between Family Status and Academic Achievement in Children"
author: 
  - Ruibo Sun
thanks: "https://github.com/ruibosun/how-parents-affect-childrens-education"
date: "`r Sys.time()`"
date-format: "12-03-2023"
abstract: "This paper explores the relationship between family status variables, such as parents' socio-economic status and educational level, and their impact on children's academic achievement and education level using the data from 2021 GSS. Previous studies have suggested that parents' education can positively influence their children's academic performance due to increased access to resources and greater involvement in their education. However, recent research has demonstrated that this relationship is complex and can be influenced by a variety of psychological and sociological factors. The findings suggest that parents' education, family income, and prestige score all have a positive correlation with children's education. Further research is needed to fully understand the complexities of this relationship and use the results to improve educational policies and programs."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

```{r,echo=FALSE}
#| include: false
#| warning: false
#| message: false
cleaned_data <- read_csv(
  file = here("inputs/data/GSS2021 2.csv"))
```

@@

>>>>

---
title: "The Relationship between Family Status and Academic Achievement in Children in U.S. from 2021"
author: 
  - Ruibo Sun
thanks: "https://github.com/ruibosun/how-parents-affect-childrens-education"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "This paper explores the relationship between family status variables, such as parents' socio-economic status and educational level, and their impact on children's academic achievement and education level using the data from 2021 GSS. Previous studies have suggested that parents' education can positively influence their children's academic performance due to increased access to resources and greater involvement in their education. However, recent research has demonstrated that this relationship is complex and can be influenced by a variety of psychological and sociological factors. The findings suggest that parents' education, family income, and prestige score all have a positive correlation with children's education. Further research is needed to fully understand the complexities of this relationship and use the results to improve educational policies and programs."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

```{r,echo=FALSE}
#| include: false
#| warning: false
#| message: false
cleaned_data <- read_csv(
  file = here("inputs/data/GSS2021.csv"))
```

@@

# Appendix

## Link to the Survey
Please view the survey by this link [link](https://forms.office.com/Pages/ResponsePage.aspx?id=JsKqeAMvTUuQN7RtVsVSEIL6CTEUDb9LuJG06wrhLr9UMTNRNUNFS0tFT0hVTVM4UVFXWDdINFY5Sy4u).

## Supplementary Survey
1.What is your gender?

- Male
- Female
- Non-binary
- Woman
- Man
- Prefer not to say

2.What is your race?

- White
- Black or African American
- Hispanic or Latino
- Asian
- Native American or Alaska Native
- Native Hawaiian or other Pacific Islander
- Other

3.Do you consider yourself as an immigrant?

- Yes
- No
- Maybe

4.US citizen

- Yes
- No

5.What is the highest level of education you have achieved?

- Less than high school
- High school diploma or equivalent
- Some college or associate degree
- Bachelor's degree
- Graduate degree or higher

6.What type of school did you attend in your teenage?

- Public school
- Private school
- Homeschool
- Other

7.High school GPA (if applicable)

8.College/University GPA (if applicable)

9.What is the highest level of education achieved by your mother and father?

- Less than high school
- High school diploma or equivalent
- Some college or associate degree
- Bachelor's degree
- Graduate degree or higher

10.What was your parents' occupation in your teenage?

- Professional/managerial
- Technical/sales
- Administrative/clerical
- Blue collar/other manual
- Other

11.What is the highest level of education completed by your mother?

- Less than high school
- High school graduate
- Some college or technical school
- Bachelor's degree
- Graduate degree (Master's or Doctorate)

12.What is the highest level of education completed by your father?

- Less than high school
- High school graduate
- Some college or technical school
- Bachelor's degree
- Graduate degree (Master's or Doctorate)

13.How involved are your parents in your education?

- Not involved
- Somewhat involved
- Moderately involved
- Highly involved

14.What is your family's income level in your teenage?

- Far above average
- Above average
- Average
- Below average
- Far below average

15.Where did you live in your teenage years?

- Rural area
- Suburban area
- Urban area

16.How much pressure do you feel from your parents to excel academically?

- None
- A little
- Moderate
- High
- Very high
